A Domain Specific Language for Functional Code Fusion for Intrusion Detection Algorithms in Wireless Sensor Networks

### 2014-09-29 paper.tex
some last-minute details

Introducing intrusion detection in wireless sensor network (WSNs) puts a strain
on the limited resources of its nodes. Fusion of the underlying algorithms can
alleviate this, but the manual and repetitive labor proves to be an
unacceptable economic burden and is error-prone. Intrusion detection algorithms
share common functionality and structure, and therefore are a prime candidate
for the application of a domain specific language (DSL). In this paper we
propose such a DSL to describe these algorithms in a formal and functional way.
This allows for the automation of the fusion of these algorithms on a
functional level though code generation. The code, produced by a prototype code
generator implementation, shows to have less impact on e.g. the execution time
of the resulting intrusion detection system and its use of the wireless
network, in comparison with a basic side-by-side implementation of the same
algorithms.

>>>>

Introducing intrusion detection in wireless sensor network (WSNs) puts a strain
on the limited resources of its nodes. Fusion of the underlying algorithms can
alleviate this, but the manual and repetitive labor proves to be an
unacceptable economic burden and is error-prone. Intrusion detection algorithms
share common functionality and structure, and therefore are a prime candidate
for the application of a domain specific language (DSL). This paper propose
such a DSL to describe these algorithms in a formal and functional way. This
allows for the automation of the fusion of these algorithms on a functional
level though code generation. The more optimally fused code, produced by a
prototype code generator implementation, shows to have less impact on e.g. the
execution time of the resulting intrusion detection system and its use of the
wireless network, in comparison with a basic side-by-side implementation of the
same algorithms.
